---
title: "APACPH-23-136: RESEARCH TREND ON STROKE CAREGIVER BURDEN, A BIBLIOMETRIC ANALYSIS"
author:
  - name: Mohd Azmi Bin Suliman
    orcid: 0000-0002-2125-3811
    email: azmi.suliman@moh.gov.my
    affiliations:
      - name: Institut Kesihatan Umum
        city: Shah Alam
        state: Selangor
        country: Malaysia
        postal-code: 40170
date: last-modified
date-format: "dddd, DD/MM/YYYY"
format: 
  html:
    theme: sandstone
    code-fold: show
    code-copy: hover
    code-overflow: wrap
    code-tools: true
    df-print: paged
    default-image-extension: svg
    embed-resources: true
    page-layout: full
    reference-location: margin
    title-block-banner: true
    title-block-style: default
    fontsize: .9em
    monofont: 'Fira Code'
execute: 
  warning: false
number-sections: true
toc: true
fig-dpi: 320
dpi: 320
---

# Data Preparation (Setup)

```{r}
#| label: setup

pacman::p_load(tidyverse, 
               bibliometrix,  # bibliometric analysis software
               janitor,       # data cleaning
               stringr,       # data wrangling – string manipulation	
               kableExtra)    # nice table

bibds_pm <- convert2df(file = "23-05-22 scopus search.bib",
                       dbsource = "scopus",
                       format = "bibtex")

bibds_pm95_10 <- bibds_pm %>% 
  filter(PY <= 2011)
bibds_pm11_22 <- bibds_pm %>% 
  filter(PY >= 2011)

bibres <- biblioAnalysis(bibds_pm, sep = ";")
bibres95_10 <- biblioAnalysis(bibds_pm95_10, sep = ";")
bibres11_22 <- biblioAnalysis(bibds_pm11_22, sep = ";")
```

# Result

## General Information

```{r}
bibres_summary <- summary(bibres, k = 25)
#plot(bibres, k = 25)
```

```{r}
#| results: hide

bibres_summary95_10 <- summary(bibres95_10, k = 25)
bibres_summary11_22 <- summary(bibres11_22, k = 25)
```


## Publication per year

```{r}
#| fig-cap: "Annual Output of Research"


subset1 <- tibble(Year = 1995:2011,
                  n = 1.5 * exp(0.08 * (1995:2011 -1995)))
subset2 <- tibble(Year = 2011:2022, 
                  n = 5.5 * exp(0.13 * (2011:2022 -2011))) 

pubnoplot <- tibble(Article = rownames(bibds_pm),
                    Year = bibds_pm$PY) %>% 
  group_by(Year) %>% 
  summarise(n = n()) %>% 
  mutate(Group = if_else(Year <= 2010, "1995-2010", "2011-2022")) %>% 
  ggplot(aes(x = Year, y = n)) +
  geom_area(alpha = .2) +
  geom_point(aes(colour = Group)) +
  geom_line() +
  geom_line(data = subset1, linetype = 2, linewidth = 1, 
            alpha = 0.4, colour = "blue") +
  geom_line(data = subset2, linetype = 4, linewidth = 1, 
            alpha = 0.4, colour = "purple") +
  geom_vline(xintercept = 2011, linetype = 3) + 
  geom_text(aes(x = 2011, y = 15, label = "Growth Spurt @ 2011", 
                angle = 90), vjust = -.5) + 
  scale_y_continuous(breaks = seq(2, 26, 4), expand = c(0, 0)) +
  scale_x_continuous(breaks = c(1995, 1999, 2003, 2007, 2011, 2015, 2019, 2022), 
                     expand = c(0, 0.2)) +
  scale_y_continuous(sec.axis = sec_axis(~ .)) +
  coord_cartesian(ylim = c(0, 24)) +
  labs(x = "Year", y = "Number of Publication") +
  scale_color_manual(values = c("blue", "purple")) +
  theme_bw() +
  theme(panel.grid = element_blank(),
        panel.border = element_blank(),
        panel.background = element_rect(fill = "transparent")) +
  guides(color = "none")

pubnoplot
```

## Top Publication (influential articles)

```{r}
#| tbl-cap: "Most Cited Articles"

tibble(bibres_summary$MostCitedPapers) %>% 
  select(DOI, TC, TCperYear) %>% 
  arrange(desc(TCperYear)) %>% 
  head(n = 10) %>% 
  kable() %>% kable_classic()
```


```{r}
#| tbl-cap: "Highest Average Cited Per Year Articles"

tibble(Title = bibds_pm$TI,
       Author = bibds_pm$AU,
       Year = bibds_pm$PY,
       DOI = bibds_pm$DI,
       Citations = bibds_pm$TC) %>% 
  mutate(across(.cols = c(Title, Author), .fns = str_to_title)) %>% 
  arrange(desc(Citations)) %>% 
  head(n=10) %>% 
  kable() %>% kable_classic()
```

## Thematic Map

```{r}
bib_thememap <- thematicMap(bibds_pm, field = "DE", n = 200, minfreq = 20, 
                            stemming = F, size = .5, n.labels = 4, repel = T)

plot(bib_thememap$map)
```

# Other (not included in poster)

## Countries

```{r}
bibres_countrylist <- bibres$Countries

bibres_countrytable <- tibble(Rank = seq_along(bibres_countrylist),
                              Country = rownames(bibres_countrylist),
                              Np = as.integer(bibres_countrylist))

bibres_countrytable

bibressum_countrytable <- tibble(Rank = 1:25,
                                 bibres_summary$TCperCountries) %>% 
  rename("Country" = "Country     ") %>% 
  mutate(Country = str_trim(Country),
         Country = fct_reorder(Country, Rank),
         `Total Citations` = as.integer(`Total Citations`),
         `Average Article Citations` = as.double(`Average Article Citations`),
         percent = `Total Citations` / sum(`Total Citations`) * 100,
         percent = round(percent,1)) %>% 
  inner_join(x = ., y = select(bibres_countrytable, Country, Np), 
             by = "Country") %>% 
  relocate(percent, .after = `Total Citations`)

bibressum_countrytable
```


```{r}
bib_concolab <- metaTagExtraction(bibds_pm, Field = "AU_CO", sep = ";")

bib_concolab_NetMatrix <- biblioNetwork(bib_concolab, analysis = "collaboration",
                                        network = "countries", sep = ";")

bib_concolab_Plot <- networkPlot(bib_concolab_NetMatrix,
                                 n = dim(bib_concolab_NetMatrix)[1],
                                 Title = "Country collaboration",
                                 type = "auto",
                                 size=20,
                                 size.cex=T,
                                 edgesize = 2,
                                 labelsize=1,
                                 #edges.min = 1,
                                 remove.isolates = T,
                                 community.repulsion = 0,
                                 cluster = "optimal"
                                 )
```

::: {.callout-tip}
## Biblioshiny

for collaboration network, using biblioshiny is nicer
:::


## Institution

```{r}
bibres_instlist <- bibres$Affiliations

bibres_insttable <- tibble(Rank = seq_along(bibres_instlist),
                           InstitutionAffiliation = rownames(bibres_instlist),
                           Np = as.integer(bibres_instlist)) %>% 
  mutate(InstitutionAffiliation = fct_reorder(InstitutionAffiliation, Rank))

bibres_insttable
```


```{r}
bib_educolab_NetMatrix <- biblioNetwork(bibds_pm, analysis = "collaboration",
                                       network = "universities", sep = ";")

bib_educolab_Plot <- networkPlot(bib_educolab_NetMatrix, 
                                 n = 100, 
                                 cluster = "optimal", 
                                 type = "auto",
                                 size.cex = F, 
                                 size = 3, 
                                 remove.multiple = F,
                                 labelsize=1, 
                                 alpha = .7, 
                                 edgesize = 1,
                                 edges.min = 2, 
                                 remove.isolates = T, 
                                 community.repulsion = 0,
                                 Title = "Institutions collaboration")

```


## Journal

```{r}
bibres_sourcelist <- bibres$Sources

bibres_sourcetable <- tibble(Rank = seq_along(bibres_sourcelist),
                             SourceJournal = rownames(bibres_sourcelist),
                             Np = as.integer(bibres_sourcelist)) %>% 
  mutate(SourceJournal = fct_reorder(SourceJournal, Rank))

bibres_sourcetable

bibres_sourcetablepercent <- bibres_sourcetable %>% 
  count(Np) %>% 
  mutate(percent = n / sum(n) * 100,
         percent = round(percent,1))

bibres_sourcetablepercent

bib_bradford <- bradford(bibds_pm)

bib_bradfordtable <- bib_bradford$table %>% 
  select(Zone, Freq, Rank) %>% 
  tibble() %>% 
  group_by(Zone) %>% 
  summarise(nSO = n(),
            nArt = sum(Freq),
            RankRange = str_c(min(Rank), max(Rank), sep = "-")) %>% 
  mutate(percent = nArt / sum(nArt) * 100,
         percent = round(percent,1))

bib_bradfordtable
```

```{r}
# bib_CRSO <- metaTagExtraction(bibds_pm, Field = "CR_SO", sep = ";")
# bib_CRSO_NetMatrix <- biblioNetwork(bib_CRSO, analysis = "co-citation", 
#                                     network = "sources", sep = ";")
# bib_CRSO_Plot <- networkPlot(bib_CRSO_NetMatrix, n = 20, 
#                              Title = "Co-citation Network", type = "auto", 
#                              size.cex = T, size = 20, remove.multiple = F,
#                              labelsize = 1, edgesize = 5, edges.min = 5, alpha = 1)
```

::: {.callout-warning}
co-citation network not available
:::

## Author

```{r}
bibds_noaufreq <- bibds_pm %>% 
  select(TI, AU, DT) %>% 
  tibble() %>% 
  mutate(no_auth = str_count(AU, pattern = ";") + 1) %>% 
  rename("paper" = "TI", "author" = "AU", "type" = "DT") %>% 
  group_by(no_auth, type) %>% 
  summarise(freq = n(), .groups = "drop") %>% 
  mutate(percent = freq / sum(freq) * 100,
         percent = round(percent,1))

bibds_noaufreq %>% 
  ggplot(aes(no_auth, freq)) + 
  geom_bar(stat = "identity") + 
  labs(x = "Number of Authors", y = "Frequency (Number of Articles)") + 
  scale_x_continuous(breaks = seq(-3,30,2)) +
  scale_y_continuous(breaks = seq(-2,40,4)) +
  theme_bw()


bibres_aulist <- bibres$Authors

bibres_autable <- tibble(Rank = seq_along(bibres_aulist),
                         Author = rownames(bibres_aulist),
                         Np = as.integer(bibres_aulist)) %>% 
  mutate(Author = fct_reorder(Author, Rank))

bibres_autable

bibres_autablepercent <- bibres_autable %>% 
  count(Np) %>% 
  mutate(percent = n / sum(n) * 100,
         percent = round(percent,1))

bibres_autablepercent
```

```{r}
# bib_AuCoupling_NetMatrix <- biblioNetwork(bibds_pm, analysis = "coupling",
#                                           network = "authors", sep = ";")
# 
# bib_AuCoupling_Plot <- networkPlot(bib_AuCoupling_NetMatrix, n = 15, 
#                                    cluster = "optimal", type = "auto", 
#                                    size.cex = T, size = 20, remove.multiple = F,
#                                    Title = "Bibliographic coupling of the authors",
#                                    alpha = .7)
```

::: {.callout-warning}
co-citation network not available
:::

## Keyword

```{r}
cbind(Rank = 1:25, bibres_summary$MostRelKeywords)
```

```{r}
# bib_kwco_NetMatrix <- biblioNetwork(bibds_pm, analysis = "co-occurrences", 
#                                      network = "keywords", sep = ";")
# 
# bib_kwco_Plot <- networkPlot(bib_kwco_NetMatrix, normalize = "association", 
#                              n = 20, Title = "Keyword Co-occurences", 
#                              cluster = "optimal", type = "fruchterman", 
#                              size.cex = T, size = 20,  remove.multiple = F, 
#                              edgesize = 7, labelsize = 3, label.cex = T, 
#                              label.n = 20, edges.min = 10)
```

::: {.callout-tip}
## Biblioshiny

for keyword co-occurence network, using biblioshiny is nicer
:::
